---
title: "Breast cancer classification using proteomic data"
author: "G9 - Huang Yi, Liu Yu, Rossen Anne Marie Nørrelykke, Spjelkavik Synne."
date: '2022-04-19'
output:
  ioslides_presentation:
  incremental: true
  widescreen: true
  smaller: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r include=FALSE}
library(tidyverse)
library(knitr)
```


## Contents

- Introduction
- Materials
  -data selection
  -merge
- Methods  
- Results and Discussion
- Conclusion
---

# Introduction
- this data was selected from the Breast cancer.based on the PAM50 gene was devide into 4 subtypes.
- in this study we try to use this dataset to detect different gene contribute to the subtype devision based on theie expression level.

## introduction
-this dataset contains 77 patients' and 3 health samples.
-Afer cleaned it we merged the 3 data and plot all the attributes basd on their subtypes.and then we decide to select some of the attributes and do PCA to see if the attribute is related to it's subtype devision.


## Slide with Plot
- t
